Making Deep Q-learning Methods Robust to Time Discretization

### 2019-01-20 paper/icml_drau/advup.tex

\begin{theorem}
	\TODO{We need a bit more details: we probably want to assume that states and actions are
	drawn from a single fixed trajectory, and that we are learning for a fixed, constant policy.}
	Let $\eta^V_\deltat = \alpha^V \deltat^\beta$ (resp. $\eta^A \deltat^\beta$) be the learning rate
	of $V$ (resp. $A$), when training on a single exploratory trajectory. Then
	\begin{itemize}
		\item If $\beta = 1$ the discrete parameter trajectories converge to continuous parameter
			trajectories as $\deltat$ goes to $0$.
		\item If $\beta < 1$, parameters grow arbitrarily large in a single timestep as $\deltat$
			goes to $0$.
		\item If $\beta > 1$, parameter trajectories shrink to a single point as 
			$\deltat$ goes to $0$. \TODO{Is that clear}
	\end{itemize}
	\label{th:cont-params}
\end{theorem}

% With this choice of learning rates, the limit SDEs are
% \begin{align}
% 	F &= A(s_t, a_t) - r_t - \log(\gamma) V(s_t) - \partial_s V(s_t) f(s_t, a_t)\nonumber\\
% 	G &= - \partial_s V(s_t, a_t) \Sigma(s_t, a_t)\nonumber\\
% 	d\theta_t &= (\alpha^V Fdt  + D \dbt)\partial_{\theta} V(s_t)\nonumber\\
% 	d\psi_t &= (\alpha^A Fdt  + D \dbt)\partial_{\psi} A(s_t, a_t)\nonumber.
% \end{align}
The full algorithm, that is referred to as \emph{Deep Advantage Updating} (DAU), can now be derived.
Pseudocode for the discrete actions algorithm is given in Alg.~\ref{alg:dau}.
Pseudocode for the continuous actions algorithm is given in the supplementary
material.

>>>>

\begin{theorem}
	\TODO{We need a bit more details: we probably want to assume that states and actions are
	drawn from a single fixed trajectory, and that we are learning for a fixed, constant policy.}
	Let $\eta^V_\deltat = \alpha^V \deltat^\beta$ (resp. $\eta^A \deltat^\beta$) be the learning rate
	of $V$ (resp. $A$), when training on a single exploratory trajectory. Then
	\begin{itemize}
		\item If $\beta = 1$ the discrete parameter trajectories converge to continuous parameter
			trajectories as $\deltat$ goes to $0$.
		\item If $\beta < 1$, parameters grow arbitrarily large in a single timestep as $\deltat$
			goes to $0$. \TODO{not quite true, in a single
			step the update is bounded. But the parameters
			become arbitrary large in an arbitrarily small
			physical time.}
		\item If $\beta > 1$, parameter trajectories become
		stationary as
			$\deltat$ goes to $0$.
	\end{itemize}
	\label{th:cont-params}
\end{theorem}

% With this choice of learning rates, the limit SDEs are
% \begin{align}
% 	F &= A(s_t, a_t) - r_t - \log(\gamma) V(s_t) - \partial_s V(s_t) f(s_t, a_t)\nonumber\\
% 	G &= - \partial_s V(s_t, a_t) \Sigma(s_t, a_t)\nonumber\\
% 	d\theta_t &= (\alpha^V Fdt  + D \dbt)\partial_{\theta} V(s_t)\nonumber\\
% 	d\psi_t &= (\alpha^A Fdt  + D \dbt)\partial_{\psi} A(s_t, a_t)\nonumber.
% \end{align}

This results in a fullly specified algorithm,
\emph{Deep Advantage Updating} (DAU).
Pseudocode for the discrete actions algorithm is given in Alg.~\ref{alg:dau}.
Pseudocode for continuous actions is given in the supplementary
material.

### 2019-01-20 paper/icml_drau/discussions.tex

\paragraph{Near continuous time reinforcement learning and RMSprop.} RMSprop~\cite{rmsprop}
estimates a batched version of the second moment of gradients via moving
averages, and divides gradient steps by the square root of this estimate.
This may interact with the learning rate scaling discussed above. In
deterministic environments, gradient noise typically scales as $\bigO(1)$ in
term of $\deltat$, as seen in \eqref{eq:approx_bellman_A}.  In that case, RMSprop
preconditioning has no effect on the suitable order of magnitude for learning
rates. However, in near continuous \emph{stochastic} environments, as in
Eq.~\ref{eq:sde}, variance of the gradient noise typically scales as
$\bigO\left(\frac{1}{\deltat}\right)$. If batch size does not depend on
$\deltat$, RMSprop preconditioning thus multiplies gradients by a factor $\bigO(\sqrt{\deltat})$,
and learning rates need only be scaled as $\alpha \sqrt{\deltat}$ instead of
$\alpha \deltat$.

>>>>

\paragraph{Near continuous time reinforcement learning and RMSprop.} RMSprop~\cite{rmsprop}
estimates a batched version of the second moment of gradients via moving
averages, and divides gradient steps by the square root of this estimate.
This may interact with the learning rate scaling discussed above. In
deterministic environments, gradients typically scale as $\bigO(1)$ in
term of $\deltat$, as seen in \eqref{eq:approx_bellman_A}.  In that case, RMSprop
preconditioning has no effect on the suitable order of magnitude for learning
rates. However, in near continuous \emph{stochastic} environments (Eq.~\ref{eq:sde}), variance of the gradients typically scales as
$\bigO\left(\frac{1}{\deltat}\right)$. With a fixed batch size,
RMSprop will multiply gradients by a factor $\bigO(\sqrt{\deltat})$. In
that case,
learning rates need only be scaled as $\alpha \,\sqrt{\deltat}$ instead of
$\alpha \,\deltat$.
